xwMOOC 딥러닝

### 2020-06-20 r-mnist-python.Rmd
compile..

```{r keras-mnist-function-object}
source_python("code/mnist-keras-function-object.py")
score <- mnist_function()

@@

>>>>

```{r keras-mnist-function-object, eval = FALSE}
source_python("code/mnist-keras-function-object.py")
score <- mnist_function()

@@

# 예측값 {#mnist-python-classifier-predict}

```{r keras-mnist-function-object-predict}
library(tidyverse)

source_python("code/mnist-keras-function-object-predict.py")
result <- mnist_function()

tibble(y_pred = result[[0]], y_label = result[[1]])

y_pred <- result[[1]]
y_label <- result[[2]]

y_pred %>% as_tibble()
y_label %>% as_tibble()
